---
title: "Group 8 Presentation"
author: "Scout Leonard"
date: "10/25/2021"
output: 
 xaringan::moon_reader
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(xaringan)
```

#Our Question

**How do population demographic factors impact lead exposure in Philadelphia?**

- Developed from an interest in an EJ question
- DataONE had environmental health data for this question specifically from a 2021 published study 

---

#[Data Management Plan](https://github.com/scoutcleonard/eds213_group8)

- **Data managers:** Alex Vand, Clarissa Boyajian, and Scout Leonard
- **Repository owner:** Scout Leonard (Clarissa and Alex are collaborators)
- This team effort calls two datasets: one which contains **lead risk factors for Philadelphia communities**, and another which contains **human demographic data.** 
  - 6 hours for the 2 datasets
  - Code to call/clean/combine data in our repo
- **Preservation plan:** We plan to save until the end of MEDS!
- No legal constraints. 

---
#Obtaining and Merging Data

--- 
#Interesting Results 

--- 
#Find us on KNB and Github! 

