---
title: "Group 8 Presentation"
author: "Scout Leonard"
date: "10/25/2021"
output: 
 xaringan::moon_reader
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(xaringan)
```

#Our Question

**How do population demographic factors impact lead exposure in Philadelphia?**

- Developed from an interest in an EJ question
- DataONE had environmental health data for this question specifically from a 2021 published study 

---

#Data Management Plan

- **Data managers:** Alex Vand, Clarissa Boyajian, and Scout Leonard
- **Repository owner:** Scout Leonard (Clarissa and Alex are collaborators)
- This team effort calls two datasets: one which contains **lead risk factors for Philadelphia communities**, and another which contains **human demographic data.** 
  - 6 hours for the 2 datasets
  - Code to call/clean/combine data in our repo
- **Preservation plan:** We plan to save until the end of MEDS!
- No legal constraints. 

---

#Obtaining and Merging Data

- Data Retrieval
  - Public Health/Lead Data: `metajam` package
    - This uses an API to download the DataONE
    - This creates the `metajam` log; stashed in out `.gitignore`
  - Census/demographic data: `censusapi` package
    - Requires an access token to control server traffic
    - `censusapi` package restricted us from pulling based on 1 county; we downloaded all of the data from state 42 before filtering
- Data Combination
  - Left joined datasets based on census tract
  - Census tract format required cleaning in lead dataset


---

#Results

---

#Data Preservation: KNB

---

##Data Preservation: Github Repo
